---
title: "Getting Started with dieroller"
author: "Lindsey Chung"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(dieroller)

```


## Roll a Die
The package `dieroller` simulates creating a die and rolling it a given number of times. It also provides functions to visualize the relative frequencies of these rolls.


## Creating a `die`

The first step to create a `die` object is to use the die() function:

```{r}
die1 = die()
die1

```

By default, `die()` creats a fair die with standard sides `1` through `6` and probabilities `1/6` for each side.

You can change the defaults with arguments `sides` and `prob`:

```{r}
loaded = die(prob = c(0.1, 0.1, 0.1, 0.1, 0.1, 0.5))
loaded

funky = die(sides = c('this', 'is', 'a', 'fun', 'funky', 'die'))
funky

```


## Rolling a Die

Once you have defined a `die` object, you can use the function `roll()` to roll your `die` a certain number of `times`. The output will be an object of class `roll`, which will contain a vector of `rolls`.

```{r}
roll100 = roll(die1, times = 100)
roll100

```

The `summary()` function gives you a nice table of freqencies:

```{r}
summary(roll100)

```

## Plot of relative frequencies

You can use the `plot()` function to create a bar graph with the relative frequencies of a series of die rolls.

```{r}
plot(roll100)

```

## Other Methods for `roll` Objects

You can use a number of other functions to manipulate `roll` objects.

The bracket subsetter will return the roll in the position specified by the bracket:

```{r}
roll100[100]

```

You can also replace specific rolls in a series:

```{r}
roll100[100] = 1
roll100

```

Finally, you can use the `+` function to add more rolls to the current series:

```{r}
roll150 = roll100 + 50
roll150

```

