---
title: "HW 02 - Shot Charts"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = '../images/')
```


## Total Shots by Player

```{r}

library(dplyr)
library(readr)
library(ggplot2)

shots = read.csv('../data/shots-data.csv', stringsAsFactors = FALSE)
shots_tib = as_tibble(shots)

total_shots = shots_tib %>%
  group_by(name) %>%
  summarise(total = n()) %>%
  arrange(desc(total))
total_shots

```


## Effective Shooting Percentage

```{r}

# Effective Shooting % by Player

effective_shooting = shots_tib %>%
  group_by(name) %>%
  summarise(total = n(), made = sum(shot_made_flag == 'made shot')) %>%
  mutate(perc_made = made/total * 100) %>%
  arrange(desc(perc_made))
effective_shooting

# 2PT Effective Shooting % by Player
effective_shooting2PT = shots_tib %>%
  filter(shot_type == '2PT Field Goal') %>%
  group_by(name) %>%
  summarise(total2PT = n(), made2PT = sum(shot_made_flag == 'made shot')) %>%
  mutate(perc_made2PT = made2PT/total2PT * 100) %>%
  arrange(desc(perc_made2PT))
effective_shooting2PT
  
# 3PT Effective Shooting % by Player
effective_shooting3PT = shots_tib %>%
  filter(shot_type == '3PT Field Goal') %>%
  group_by(name) %>%
  summarise(total3PT = n(), made3PT = sum(shot_made_flag == 'made shot')) %>%
  mutate(perc_made3PT = made3PT/total3PT * 100) %>%
  arrange(desc(perc_made3PT))
effective_shooting3PT

```


## Shooting Distance

```{r}

distances = shots_tib %>%
  group_by(shot_distance) %>%
  summarise(made_shot_prop = (sum(shot_made_flag == 'made shot')) / n())
distances

```

```{r distance_effectiveness}

ggplot(data = distances, aes(x = shot_distance, y = made_shot_prop)) +
  geom_point()

```

This scatterplot shows the proportion of made shots at each shot distance.

- Observations:
    - high proportion of shots made from very close to the basket (0 or 1 foot)
    - generally within the same range of medium propotions (0.3 to 0.55) of shots made from 3 feet to 23 feet
    - generally no shots made from distaces 24 feet or greater (with one outlier)
- From the data, it can not be confirmed overall that the shorter the distance, the more effective shots. This can only be confirmed for extremely close shots.
- Threshold beyond which chance of making a shot is pretty much 0: 35 feet
- Distances 0 to 2 feet have a percentage of making the shot of above 50%. Some other specific distances have efficacy percentages of above 50%, but when looked at with the data points around them, it would not be expected that the range of percentages would be above 50%.


## Total Number of Shots by Minute of Occurence

```{r}

shots_minute = shots_tib %>%
  group_by(name, minute) %>%
  summarise(shots_by_minute = n())

```

```{r shots_by_min}

shots_by_min = ggplot(data = shots_minute, aes(x = minute, y = shots_by_minute)) +
  geom_rect(mapping = aes(xmin = 0, xmax = 12, ymin = -2, ymax = 60), fill = 'grey90') +
  geom_rect(mapping = aes(xmin = 24, xmax = 36, ymin = -2, ymax = 60), fill = 'grey90') +
  geom_point(color = 'dodgerblue', alpha = 0.8) +
  facet_wrap(~ name) +
  scale_x_continuous(breaks = c(1, 12, 24, 36, 48), limits = c(0, 48)) +
  theme_minimal() +
  scale_y_continuous(name = 'total number of shots', breaks = c(0, 20, 40), limits = c(-2, 60)) +
  geom_path(color = 'dodgerblue', alpha = 0.5) +
  ggtitle("Total number of shots (by minute of occurence)")
shots_by_min

```

This graphich shows the total number of shots taken at each minute of the game. It is facetted by player.




